\documentclass{beamer}

\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usefonttheme{serif}


\newcommand{\Nat}{\mathbb{N}}

\title{Graphs}%\texorpdfstring{$\mathbb{N}$}}
\subtitle{The math kind, not the stonk kind}
\date{Febuary 22\textsuperscript{nd}, 2021}

\usetheme{jmct}

\usepackage{calc}

\newcommand{\textover}[3][l]{%
 % #1 is the alignment, default l
 % #2 is the text to be printed
 % #3 is the text for setting the width
 \makebox[\widthof{#3}][#1]{#2}%
 }

\newcommand{\blueit}[1]{%
  {\color{dark-lucid-blue}#1}%
}
\newcommand{\blueite}[1]{%
  \blueit{\emph{#1}}%
}


\newcommand{\myquote}[3]{
  ``#1''
  \vspace{3pt}
  \hrule
  \begin{flushright}
  --- \blueit{\emph{#2}}, \emph{#3}
  \end{flushright}
}

\begin{document}
	\frame {
		\titlepage
	}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{This Lecture}
    Tiny demo of SQL via Python, then on to Graphs
  }

  \frame{
    \frametitle{Before we start...}
      \begin{enumerate}
        \item<2 -> Laura is our moderator again, say high!
        \item<3 -> Website updates
        \item<4 -> Quiz question \#4
        \item<5 -> Final Projects!
      \end{enumerate}
  }

  \frame{
    \frametitle{Website updates}
      \begin{enumerate}
        \item<2 -> My UMD email should be easier to find, apologies about that.
        \item<3 -> TA office hours have been updated.
      \end{enumerate}
  }


  \frame{
    \frametitle{Quiz Question \#4}
      \begin{enumerate}
        \item<2 -> This was not meant to cause panic.
        \item<3 -> There are \emph{many} more correct answer (technically an infinite number of correct answers). You will \blueit{all get your points}.
        \item<4 -> Who did this to you?
      \end{enumerate}
  }

  \frame{
    \frametitle{Final Projects}
      \begin{enumerate}
        \item<2 -> On Wednesday we will talk a bit about final projects
        \item<3 -> We will go over some good examples from previous semesters (currently waiting on permission from those students before I post on the website)
        \item<4 -> Come to the lecture if you want to discuss :D
      \end{enumerate}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% SQL Example
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{SQLite3 from Python}
      \onslide<2->{To the Notebook}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Thanks for your time!}
  }

\end{document}
