\documentclass{beamer}

\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usefonttheme{serif}


\newcommand{\Nat}{\mathbb{N}}

\title{Data Science}%\texorpdfstring{$\mathbb{N}$}}
\subtitle{\blueit{Post-Midterm Review}}
\date{April 5\textsuperscript{th}, 2021}

\usetheme{jmct}

\usepackage{calc}

\newcommand{\textover}[3][l]{%
 % #1 is the alignment, default l
 % #2 is the text to be printed
 % #3 is the text for setting the width
 \makebox[\widthof{#3}][#1]{#2}%
 }

\newcommand{\blueit}[1]{%
  {\color{dark-lucid-blue}#1}%
}
\newcommand{\blueite}[1]{%
  \blueit{\emph{#1}}%
}


\newcommand{\myquote}[3]{
  ``#1''
  \vspace{3pt}
  \hrule
  \begin{flushright}
  --- \blueit{\emph{#2}}, \emph{#3}
  \end{flushright}
}

\begin{document}
	\frame {
		\titlepage
	}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Getting Right to it}
      \begin{enumerate}
        \item<2 -> Midterms and project 2 are being graded as quickly as possible
        \item<3 -> Final Project rubric is up
        \item<4 -> We are going to change the course a bit.
      \end{enumerate}
  }

  \frame{
    \frametitle{Exam Discussion}
      Common issues (so far):
      \begin{enumerate}
        \item<2 -> MAR/MNAR/MCAR
        \item<3 -> Going from definition of a Graph (and operations) \emph{mathematically} to its meaning
      \end{enumerate}
  }


  \frame{
    \frametitle{Final Project}
      Rubric is up, but we will discuss here.
      \begin{enumerate}
        \item<2 -> Unlike projects, assignment must be submitted by 4pm EDT.
        \item<3 -> Groups of up to 3 are allowed.
        \item<4 -> We will help match-make groups as part of Project 3 (to be released later this week)
        \item<5 -> To the rubric!
      \end{enumerate}
  }


  \frame{
    \frametitle{Changes in how course will be run}
      Thank you all for your feedback, it is very helpful.
      \begin{enumerate}
        \item<2 -> Many common themes
        \item<3 -> Some not-so-common suggestions
      \end{enumerate}
  }

  \frame{
    \frametitle{How we are going to use the feedbac}
      \begin{enumerate}
        \item<2 -> For anything that is `not up to debate' (5\%+ and aligns
            with course goals), we are going to try and do starting immediately
        \item<3 -> Many students just don't agree, which can be hard to address,
            for example:
        \begin{enumerate}
          \item<4 -> Faster pace
          \item<5 -> Slower pace
        \end{enumerate}
        \item<6 -> But on several things there is wide consensus, let's look at the top 3.
      \end{enumerate}
  }

  
  \frame{
    \frametitle{Lectures}
      Feedback on lectures tended to align with one of the following:
      \begin{enumerate}
        \item<2 -> Lectures need to be more focused
        \item<3 -> Other students are making it difficult to ask questions(!)
        \item<4 -> Lecturer gets derailed too easily
        \item<5 -> THe desire for lectures to be more focused was \blueit{by far}
                   the most common concern/request/suggestion.
      \end{enumerate}
  }

  \frame{
    \frametitle{How material is covered}
      \begin{enumerate}
        \item<2 -> More worked-through examples in class
        \item<3 -> Some wanted more details on the slides
        \item<4 -> Some wanted more code examples
      \end{enumerate}
  }

  \frame{
    \frametitle{Projects}
      \begin{enumerate}
        \item<2 -> Some wanted more time
        \item<3 -> Some wanted the projects to be split up into smaller chunks
        \item<4 -> Some wanted more projects
        \item<5 -> Many wanted more clarity on how to proceed
      \end{enumerate}
  }

  \frame{
    \frametitle{Looking forward}
      \begin{enumerate}
        \item<2 -> We have two industry folks coming in (one is committed the other is close)
        \item<3 -> We will have more worked-through notebooks in class
        \item<4 -> Lecture moderation will be stricter.
        \item<5 -> Staff and I will consider requests regarding the projects,
          but I cannot commit at this moment.
      \end{enumerate}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Thanks for your time!}

     :) 
  }


\end{document}
