\documentclass[handout]{beamer}

\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usepackage{tikz}
\usefonttheme{serif}


\newcommand{\Nat}{\mathbb{N}}

\title{Data Science}%\texorpdfstring{$\mathbb{N}$}}
\subtitle{\blueit{Ethics}}
\date{May 10, 2021}

\usetheme{jmct}

\usepackage{calc}

\newcommand{\textover}[3][l]{%
 % #1 is the alignment, default l
 % #2 is the text to be printed
 % #3 is the text for setting the width
 \makebox[\widthof{#3}][#1]{#2}%
 }

\newcommand{\blueit}[1]{%
  {\color{dark-lucid-blue}#1}%
}
\newcommand{\blueite}[1]{%
  \blueit{\emph{#1}}%
}
\newcommand{\redit}[1]{%
  {\color{my-magenta}#1}%
}


\newcommand{\myquote}[3]{
  ``#1''
  \vspace{3pt}
  \hrule
  \begin{flushright}
  --- \blueit{\emph{#2}}, \emph{#3}
  \end{flushright}
}

\begin{document}
	\frame {
		\titlepage
	}

\newcommand{\withwidth}[2]{%
  \makebox[\widthof{#2}][c]{#1}%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Goals for today}
    Get you thinking about the ethics of doing Data Science
    \begin{enumerate}
      \item<2 -> This is not about \blueite{morals}, lots of definitions of these things, for us:
      \begin{enumerate}
        \item<3 -> Morals: how you, individually, determine what's right or wrong
        \item<4 -> Ethics: moral principals that govern a person's behavior
                   \blueite{when conducting an activity in a professional capacity}
      \end{enumerate}
      \item<5 -> I can't tell you what's right or wrong, that's up to your moral worldview
      \item<6 -> I can tell you what the Data Science community is discussing as part of their ethical framework
    \end{enumerate}
  }

  \frame{
    \frametitle{Statistical Inference}
    We've concerned ourselves with building \redit{models}
    \begin{enumerate}
      \item<2 -> Models are used to go from world of `data' back to something we can change about the world
      \item<3 -> If we don't intend on our models being actionable, why have them?
      \item<4 -> Things we may conclude from a model:
      \begin{enumerate}
        \item<5 -> An estimate
        \item<6 -> rejection of a hypothesis
        \item<7 -> Clustering/classification of data points into groups
      \end{enumerate}
    \end{enumerate}
  }

  \frame{
    \frametitle{Sampling}
    We often can't know all the data out there, so we have to \blueite{sample}
    \begin{enumerate}
      \item<2 -> Usually, we want a random sample
      \item<3 -> When might we not want a random sample?
      \item<4 -> When gather data, (e.g. sampling the population), we have to be careful
      \begin{enumerate}
        \item<5 -> How were questions worded?
        \item<6 -> How did you poll people?
        \item<7 -> How is missing data handled?
      \end{enumerate}
    \end{enumerate}
  }

  \frame{
    \frametitle{Potential Sources of Bias}
    \begin{enumerate}
      \item<2 -> Sample Bias
      \begin{enumerate}
        \item<3 -> Selection Bias: some subjects more likely to be selected
        \item<4 -> Volunteer Bias: people who volunteer are not represenatative
        \item<5 -> Nonresponse Bias: people who decline to be interviewed
      \end{enumerate}
      \item<6 -> Survey/Response Bias
      \begin{enumerate}
        \item<7 -> Interviewer Bias
        \item<8 -> Acquiesence Bias: tendency to agree with all questions
        \item<9 -> Social Desirability Bias: Reluctance to admit to embarassing things
      \end{enumerate}
      \item<10 -> Confirmation Bias
      \item<11 -> Anchor Bias: you might say yes to something because a worse alternative was shown first.
    \end{enumerate}
  }

  \frame{
    \frametitle{Potential Sources of Bias}
    How do clinical trials work (often see as the gold standard)
    \begin{enumerate}
      \item<2 -> Some receive treatment, others in control group
      \item<3 -> Each group is picked completely at random
      \item<4 -> Considerations
      \begin{enumerate}
        \item<5 -> Only ethical of alternatives have a good basis (i.e. we don't ask folks to \emph{start} smoking for a trial)
        \item<6 -> Very expensive
        \item<7 -> Sometimes impossible!
      \end{enumerate}
      \item<8 -> What about how people `opt in'?
      \item<9 -> Social networks run trials on us all the time, is that okay?
    \end{enumerate}
  }



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Final Thoughts}
    
    \begin{enumerate}
      \item<2 -> No easy answers
      \item<3 -> Play, explore, think
      \item<4 -> Use off-the-shelf technologies wherever possible
      \item<5 -> Think about possible introduction of biases and be skeptical of `clear' results
    \end{enumerate}

  }

  \frame{
    \frametitle{Course Evals}
    
    \begin{enumerate}
      \item<2 -> If you're able, do the course evals
      \item<3 -> I try to take feedback seriously (though feedback doesn't always agree!)
    \end{enumerate}

  }
  \frame{
    \frametitle{Thanks for your time!}

     Have a good summer!
  }


\end{document}
