\documentclass{beamer}

\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usefonttheme{serif}


\newcommand{\Nat}{\mathbb{N}}

\title{\_ Data 3: Deal with it}%\texorpdfstring{$\mathbb{N}$}}
\subtitle{\blueit{Data Science, Spring 2021}}
\date{March 10\textsuperscript{th}, 2021}

\usetheme{jmct}

\usepackage{calc}

\newcommand{\textover}[3][l]{%
 % #1 is the alignment, default l
 % #2 is the text to be printed
 % #3 is the text for setting the width
 \makebox[\widthof{#3}][#1]{#2}%
 }

\newcommand{\blueit}[1]{%
  {\color{dark-lucid-blue}#1}%
}
\newcommand{\blueite}[1]{%
  \blueit{\emph{#1}}%
}


\newcommand{\myquote}[3]{
  ``#1''
  \vspace{3pt}
  \hrule
  \begin{flushright}
  --- \blueit{\emph{#2}}, \emph{#3}
  \end{flushright}
}

\begin{document}
	\frame {
		\titlepage
	}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Before we start...}
      \begin{enumerate}
        \item<2 -> Our mod of the day.
        \item<3 -> Project 2
      \end{enumerate}
  }

  \frame{
    \frametitle{Our moderator}
      \begin{enumerate}
        \item<2 -> Anubhav!
      \end{enumerate}
  }


  \frame{
    \frametitle{Project 2}
      \begin{enumerate}
        \item<2 -> If you have not started, you should start.
        \item<3 -> It is \blueit{not} expected that you work through spring break, but that assumes that you already started!
        \item<4 -> Nothing will be accepted after 11:59pm EDT\footnote{Notice the timezone}
      \end{enumerate}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Single Imputation}
      How do we \blueit{deal} with Missing Data? Some thoughts:
      \begin{enumerate}
        \item<2 -> Mean imputation: use the average of all observed cases
        \item<3 -> Hot-deck imputation: Use an observed value from a different row
        \item<4 -> Last Observation Carried Forward (LOCF): in an ordered dataset fill a missing value with its neighbor
      \end{enumerate}
  }

  \frame{
    \frametitle{Single Imputation}
      Thought?
      \onslide<2>{These are not always great (mostly used to deal with constraints we don't face anymore)}
      \begin{enumerate}
        \item<1 -> Mean imputation: use the average of all observed cases
        \item<1 -> Hot-deck imputation: Use an observed value from a different row
        \item<1 -> Last Observation Carried Forward (LOCF): in an ordered dataset fill a missing value with its neighbor
      \end{enumerate}
  }

  \frame{
    \frametitle{Imputation}
      We have a lot of processing power on our hands... how can we do better?
      \begin{enumerate}
        \item<2 -> Any thoughts?
      \end{enumerate}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Thanks for your time!}

     :) 
  }


\end{document}
