\documentclass{beamer}

\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usefonttheme{serif}


\newcommand{\Nat}{\mathbb{N}}

\title{Summary Statistics}%\texorpdfstring{$\mathbb{N}$}}
\subtitle{\blueit{Exploring Data}}
\date{Febuary 24\textsuperscript{nd}, 2021}

\usetheme{jmct}

\usepackage{calc}

\newcommand{\textover}[3][l]{%
 % #1 is the alignment, default l
 % #2 is the text to be printed
 % #3 is the text for setting the width
 \makebox[\widthof{#3}][#1]{#2}%
 }

\newcommand{\blueit}[1]{%
  {\color{dark-lucid-blue}#1}%
}
\newcommand{\blueite}[1]{%
  \blueit{\emph{#1}}%
}


\newcommand{\myquote}[3]{
  ``#1''
  \vspace{3pt}
  \hrule
  \begin{flushright}
  --- \blueit{\emph{#2}}, \emph{#3}
  \end{flushright}
}

\begin{document}
	\frame {
		\titlepage
	}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Where are we?}
    \onslide<2->{So far we've looked at how we can represent and manipulate data.}
    \onslide<3->{Now we're going to start looking at how we can \blueit{explore} the data.}
  }

  \frame{
    \frametitle{Before we start...}
      \begin{enumerate}
        \item<2 -> Our mod of the day.
        \item<3 -> Website (and repo) updates
        \item<4 -> Quiz question \#4
        \item<5 -> Final Projects!
      \end{enumerate}
  }

  \frame{
    \frametitle{Our moderator}
      \begin{enumerate}
        \item<2 -> Anubhav, BT.
        \item<3 -> Currently a Masters student working on research in Computer Vision
        \item<4 -> Be respectful
      \end{enumerate}
  }

  \frame{
    \frametitle{Website updates}
      \begin{enumerate}
        \item<2 -> There's a new repo!
        \item<3 -> I will probably shift from linking to files directly to link to that repo...
        \item<4 -> unless someone likes having the files linked as they were before
      \end{enumerate}
  }


  \frame{
    \frametitle{Quiz Question \#4}
      \begin{enumerate}
        \item<2 -> I personally looked at every quiz submission's question \#4
        \item<3 -> If you still feel that you should get a point, email me
      \end{enumerate}
  }

  \frame{
    \frametitle{Final Projects}
      \begin{enumerate}
        \item<2 -> Students will have the chance to request a group
        \item<3 -> I have some examples to show you
      \end{enumerate}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{What are we doing today and Monday?}
      \begin{enumerate}
        \item<2 -> We want \emph{descriptive statistics}
        \item<3 -> For a variable, what does this mean?
        \item<4 -> What are \emph{correlation} of two variables?
      \end{enumerate}
      
  }

  \frame{
    \frametitle{Description for a variable}
      We have two main descriptors:
      \begin{enumerate}
        \item<2 -> \blueit{Location}: mean, median, mode
        \item<3 -> \blueit{Dispertion}: variance, standard deviation
      \end{enumerate}
      
  }



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\end{document}
