\documentclass{beamer}

\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage{stmaryrd}
\usepackage{graphicx}
\usefonttheme{serif}


\newcommand{\Nat}{\mathbb{N}}

\title{Pandas + SQL}%\texorpdfstring{$\mathbb{N}$}}
\subtitle{Tidy Data}
\date{Febuary 17\textsuperscript{st}, 2021}

\usetheme{jmct}

\usepackage{calc}

\newcommand{\textover}[3][l]{%
 % #1 is the alignment, default l
 % #2 is the text to be printed
 % #3 is the text for setting the width
 \makebox[\widthof{#3}][#1]{#2}%
 }

\newcommand{\blueit}[1]{%
  {\color{dark-lucid-blue}#1}%
}
\newcommand{\blueite}[1]{%
  \blueit{\emph{#1}}%
}


\newcommand{\myquote}[3]{
  ``#1''
  \vspace{3pt}
  \hrule
  \begin{flushright}
  --- \blueit{\emph{#2}}, \emph{#3}
  \end{flushright}
}

\begin{document}
	\frame {
		\titlepage
	}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Intro
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{This Lecture}
    Some more thoughts on Pandas and SQL
  }

  \frame{
    \frametitle{Before we start...}
      \begin{enumerate}
        \item<2 -> Say hello to the mods
        \item<3 -> Some updates
      \end{enumerate}
  }

  \frame{
    \frametitle{Today's Moderator}
      \begin{enumerate}
        \item<2 -> Laura!
        \item<3 -> Currently a first-year grad student at UMD
        \item<4 -> ...also did her undergrad at UMD
      \end{enumerate}
  }

  \frame{
    \frametitle{Some updates}
      \begin{enumerate}
        \item<2 -> New docker image!
        \item<3 -> Prettify is making things ugly
      \end{enumerate}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Making DataFrames from the web}
      On Tuesday I was asked about this and said that I wouldn't be showing an example, but I can show an example today!

      \onslide<2->{To the Notebook}
  }

  \frame{
    \frametitle{Melting?!?!}
    Some students were confused about Melting (from the reading, you should be doing the reading!)
    \onslide<2->{I made a Notebook to explain!}
  }

  \frame{
    \frametitle{SQL}
      One of the most important DSLs.
      \begin{enumerate}
        \item<2 -> SQL: Working with \emph{structured} data
        \item<3 -> More specifically: \blueit{relational data}
        \item<4 -> As a rough guide: Think tuples!
      \end{enumerate}
  }

  \frame{
    \frametitle{SQL vs Pandas}
      Many pixels have been used in this debate. My take:
      \begin{enumerate}
        \item<2 -> If you have a choice, choose the one you're most comfortable with
        \item<3 -> If you don't have a choice, you use the one you have to
        \item<4 -> There are many situations where the choice is beyond your control (i.e. not just because a manager makes you)
      \end{enumerate}
  }

  \frame{
    \frametitle{SQL}
      Tables are important! \vspace{1cm}
  
    \onslide<2 -> {
  \begin{tabular}{|c|c|c|c|}
  \hline
  ID & Age & Weight (kg) & Height (cm) \\ \hline
  1 & 12.2 & 42.3 & 146.1 \\
  2 & 11.0 & 40.8 & 143.8 \\
  3 & 15.6 & 65.3 & 165.3 \\
  4 & 35.1 & 84.2 & 185.8 \\ \hline
  
  \end{tabular}} \vspace{1cm}

  \onslide<3->{We've got \blueit{Labels}, \blueit{Variables}, and \blueit{Observations}}
  }

  \begin{frame}[fragile]
    \frametitle{SQL: Primary Keys}
      Primary Keys: Unique identifier for \blueit{one observation} in \blueit{one table}.
      \vspace{1cm}

    \onslide<2 -> {
  \begin{tabular}{|c|c|c|c|c|}
  \hline
  ID & Age & Weight (kg) & Height (cm) & Nationality \\ \hline
  1 & 12.2 & 42.3 & 146.1 & 1 \\
  2 & 11.0 & 40.8 & 143.8 & 2 \\
  3 & 15.6 & 65.3 & 165.3 & 5 \\
  4 & 35.1 & 84.2 & 185.8 & 3 \\ \hline
  
  \end{tabular}} \vspace{1cm}

    \onslide<3->{When the primary key \emph{from another table} is used in a table, like above, we call them \blueit{foreign keys}}
   
  \end{frame}


  \frame{
    \frametitle{High-level view: Cons}
      SQL is very powerful, but has some downsides
      \begin{enumerate}
        \item<2 -> You have to think about the `schema' beforehand
        \item<3 -> Some people don't like SQL (the language)
        \item<4 -> YATTL :(
      \end{enumerate}
  }

  \frame{
    \frametitle{High-level view: Pros}
      SQL is very powerful, more power is more gooder
      \begin{enumerate}
        \item<2 -> Implementations are \emph{very} good
        \item<3 -> Schemas are important, thinking about them ahead of time is good!
        \item<4 -> You can share data with folks across different tech stacks!
        \item<5 -> The same system can process small, medium, large, huge amounts of data.
      \end{enumerate}
  }

  \frame{
    \frametitle{High-level view: Implementations}
      SQL is very powerful, but it's not one thing
      \begin{enumerate}
        \item<2 -> SQLite: The most popular database ever. \blueit{By far.}, great for small/medium datasets
        \item<3 -> MySQL/MariaDB: Lots of documentation, very common for the web.
        \item<4 -> PostgreSQL: Fantastic for large amounts of data, `industrial strength'
      \end{enumerate}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%%% Conclusion
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

  \frame{
    \frametitle{Thanks for your time!}
  }

\end{document}
